---
title: "TX ED GV"
author: "Neel Singh"
date: "2026-01-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries
```{r}
library(tidyverse)
library(tidyverse)
library(readxl)
library(readr)
library(tidyverse)
```

## Import Data

# THCIC Import
```{r}
THCIC <- readRDS("RDS/ED_asthma.rds") %>% 
  # Remove observations with no geolocation data and living outside of TX
  filter(!is.na(PAT_ADDR_CENSUS_BLOCK_GROUP),
         substr(PAT_ADDR_CENSUS_BLOCK_GROUP, 1, 2) == "48") %>%
  # make patient age numeric and add pediatric/adult categories
  mutate(PAT_AGE_YEARS = as.numeric(PAT_AGE_YEARS),
         AgeCat = ifelse(PAT_AGE_YEARS < 18, "Pediatric", "Adult"))

gc()
```

# ACS Covariates Import
```{r}
ACSCovariates <- readRDS("Covariates.rds")

gc()
```

# ACS Population Import
```{r}
Population <- readRDS("TXPopulation.rds")

gc()
```

# Shootings Import
```{r}
Shootings <- readRDS("ShootingsTX.rds")

ShootingsAdj <- Shootings %>% left_join(Population, by = "GEOID")

ShootingsAdj <- ShootingsAdj %>% select(GEOID, shootings, fatal_shootings, nonfatal_shootings, TotalPop) %>%
  filter(TotalPop > 0) %>%
  mutate(ShootingsPBIR = shootings / TotalPop * 10000) %>%
  select(GEOID, ShootingsPBIR, shootings, fatal_shootings, nonfatal_shootings)

gc()
```

# USDA RUCA Import
```{r}
RUCACensus2010 <- read_excel("RUCACensus2010.xlsx", 
    skip = 1) %>% # rename GEOID and RUCA columns
  rename("GEOID" = "State-County-Tract FIPS Code (lookup by address at http://www.ffiec.gov/Geocode/)",
         "RUCA" = "Primary RUCA Code 2010") %>%
  # select only necessary columns
  select(GEOID, RUCA)

gc()
```

# Pollution Data Import
```{r}
Pollution <- read_csv("CACESPollutionCensus2010.csv")

Pollution <- Pollution %>% 
  rename("GEOID" = "fips") %>%
  mutate(GEOID = as.character(GEOID), year = as.character(year)) %>%
  filter(year %in% c("2016", "2017", "2018", "2019")) %>%
  select(GEOID, pollutant, pred_wght) %>%
  group_by(GEOID, pollutant) %>%
  summarise(pred_wght = mean(pred_wght, na.rm = T
  ), .groups = "drop") %>%
  pivot_wider(names_from = pollutant, values_from = pred_wght)

gc()
```

# Join Covariates
```{r}
Covariates <- ShootingsAdj %>% 
  left_join(Pollution, by = "GEOID") %>% 
  left_join(ACSCovariates, by = "GEOID") %>% 
  left_join(Population, by = "GEOID") %>% 
  mutate(BlackPct = BlackPop / TotalPop, WhitePct = WhitePop / TotalPop, HispanicPct = HispanicPop / TotalPop)
```

## Shape Data

# Clean THCIC GEOID Variable
```{r}
# Create 11-digit State-County-Tract GEOID Variable within THCIC
THCIC <- THCIC %>%
  mutate(GEOID = substr(THCIC$PAT_ADDR_CENSUS_BLOCK_GROUP, 1, 11))

# Remove tracts outside of sufficiently urban RUCAs
THCIC <- THCIC %>%
  left_join(RUCACensus2010, by = "GEOID") %>%
  filter(RUCA %in% c("1"))

# Remove tracts without shooting exposure
THCIC <- THCIC %>% 
  left_join(ShootingsAdj, by = "GEOID") %>%
  filter(!is.na(ShootingsPBIR)) %>%
  select(-c("ShootingsPBIR", "shootings", "fatal_shootings", "nonfatal_shootings"))

# Split into THCIC for Peds and Adults
THCICPeds <- THCIC %>%
  filter(AgeCat == "Pediatric")

THCICAdult <- THCIC %>%
  filter(AgeCat == "Adult")
```


# Split into race stratified datasets
```{r}
### Total

## White
THCICWhite <- THCIC %>% filter(RACE == 4, 
                               ETHNICITY == 2) # White not Hispanic

## Black
THCICBlack <- THCIC %>% filter(RACE == 3,
                               ETHNICITY == 2) # Black not Hispanic

## Hispanic 
THCICHispanic <- THCIC %>% filter(ETHNICITY == 1) # All Hispanic

### Peds

## White Peds
THCICWhitePeds <- THCICPeds %>% filter(RACE == 4, 
                               ETHNICITY == 2) # White not Hispanic

## Black Peds
THCICBlackPeds <- THCICPeds %>% filter(RACE == 3,
                               ETHNICITY == 2) # Black not Hispanic

## Hispanic Peds
THCICHispanicPeds <- THCICPeds %>% filter(ETHNICITY == 1) # All Hispanic

### Adults

## White Adult
THCICWhiteAdult <- THCICAdult %>% filter(RACE == 4, 
                               ETHNICITY == 2) # White not Hispanic

## Black Adult
THCICBlackAdult <- THCICAdult %>% filter(RACE == 3,
                               ETHNICITY == 2) # Black not Hispanic

## Hispanic Adult
THCICHispanicAdult <- THCICAdult %>% filter(ETHNICITY == 1) # All Hispanic
```

## Analyze Data

# Generate Count of ED Visits Per Census Tract
```{r}
## Total
THCICEDCount <- THCIC %>%
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICBlackEDCount <- THCICBlack %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICHispanicEDCount <- THCICHispanic %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICWhiteEDCount <- THCICWhite %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

## Pediatric
THCICPedsEDCount <- THCICPeds %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICBlackPedsEDCount <- THCICBlackPeds %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICHispanicPedsEDCount <- THCICHispanicPeds %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICWhitePedsEDCount <- THCICWhitePeds %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

## Adult

THCICAdultEDCount <- THCICAdult %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICBlackAdultEDCount <- THCICBlackAdult %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICHispanicAdultEDCount <- THCICHispanicAdult %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")

THCICWhiteAdultEDCount <- THCICWhiteAdult %>% 
  group_by(GEOID) %>%
  summarise("TotalEDCount" = n(),
            .groups = "drop")
```

# Generate Population-Based Incidence Rates
```{r}
## Total

THCICPBIR <- THCICEDCount %>% 
  left_join(Population %>% select(GEOID, TotalPop), by = "GEOID") %>%
  filter(TotalPop > 0) %>%
  mutate(PBIR = TotalEDCount / TotalPop * 10000)

THCICBlackPBIR <- THCICBlackEDCount %>% 
  left_join(Population %>% select(GEOID, BlackPop), by = "GEOID") %>%
  filter(BlackPop > 0) %>%
  mutate(PBIR = TotalEDCount / BlackPop * 10000)

THCICHispanicPBIR <- THCICHispanicEDCount %>% 
  left_join(Population %>% select(GEOID, HispanicPop), by = "GEOID") %>%
  filter(HispanicPop > 0) %>%
  mutate(PBIR = TotalEDCount / HispanicPop * 10000)

THCICWhitePBIR <- THCICWhiteEDCount %>% 
  left_join(Population %>% select(GEOID, WhitePop), by = "GEOID") %>%
  filter(WhitePop > 0) %>%
  mutate(PBIR = TotalEDCount / WhitePop * 10000)

## Pediatrics

THCICPedsPBIR <- THCICPedsEDCount %>% 
  left_join(Population %>% select(GEOID, TotalChildPop), by = "GEOID") %>%
  filter(TotalChildPop > 0) %>%
  mutate(PBIR = TotalEDCount / TotalChildPop * 10000)

THCICBlackPedsPBIR <- THCICBlackPedsEDCount %>% 
  left_join(Population %>% select(GEOID, BlackChildPop), by = "GEOID") %>%
  filter(BlackChildPop > 0) %>%
  mutate(PBIR = TotalEDCount / BlackChildPop * 10000)

THCICHispanicPedsPBIR <- THCICHispanicPedsEDCount %>% 
  left_join(Population %>% select(GEOID, HispanicChildPop), by = "GEOID") %>%
  filter(HispanicChildPop > 0) %>%
  mutate(PBIR = TotalEDCount / HispanicChildPop * 10000)

THCICWhitePedsPBIR <- THCICWhitePedsEDCount %>% 
  left_join(Population %>% select(GEOID, WhiteChildPop), by = "GEOID") %>%
  filter(WhiteChildPop > 0) %>%
  mutate(PBIR = TotalEDCount / WhiteChildPop * 10000)

# Adult

THCICAdultPBIR <- THCICAdultEDCount %>% 
  left_join(Population %>% select(GEOID, TotalAdultPop), by = "GEOID") %>%
  filter(TotalAdultPop > 0) %>%
  mutate(PBIR = TotalEDCount / TotalAdultPop * 10000)

THCICBlackAdultPBIR <- THCICBlackAdultEDCount %>% 
  left_join(Population %>% select(GEOID, BlackAdultPop), by = "GEOID") %>%
  filter(BlackAdultPop > 0) %>%
  mutate(PBIR = TotalEDCount / BlackAdultPop * 10000)

THCICHispanicAdultPBIR <- THCICHispanicAdultEDCount %>% 
  left_join(Population %>% select(GEOID, HispanicAdultPop), by = "GEOID") %>%
  filter(HispanicAdultPop > 0) %>%
  mutate(PBIR = TotalEDCount / HispanicAdultPop * 10000)

THCICWhiteAdultPBIR <- THCICWhiteAdultEDCount %>% 
  left_join(Population %>% select(GEOID, WhiteAdultPop), by = "GEOID") %>%
  filter(WhiteAdultPop > 0) %>%
  mutate(PBIR = TotalEDCount / WhiteAdultPop * 10000)
```

# Generate Summary Statistics
```{r}
## Gun Violence

ShootingsPBIRSummary <- THCICPBIR %>% 
  left_join(ShootingsAdj, by = "GEOID") %>%
  summarise(
    Name = "ShootingsPBIR",
    TotalAREDV = sum(shootings),
    TotalPopAtRisk = sum(TotalPop),
    MeanAREDV = mean(ShootingsPBIR),
    SDAREDV = sd(ShootingsPBIR),
    MedianAREDV = median(ShootingsPBIR),
    IQRAREDV = IQR(ShootingsPBIR),
    Min = min(ShootingsPBIR),
    Max = max(ShootingsPBIR)
)

## Total

THCICPBIRSummary <- THCICPBIR %>% summarise(
  Name = "THCICPBIR",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(TotalPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICBlackPBIRSummary <- THCICBlackPBIR %>% summarise(
  Name = "THCICBlack",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(BlackPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICHispanicPBIRSummary <- THCICHispanicPBIR %>% summarise(
  Name = "THCICHispanic",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(HispanicPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICWhitePBIRSummary <- THCICWhitePBIR %>% summarise(
  Name = "THCICWhite",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(WhitePop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

## Pediatrics

THCICPedsPBIRSummary <- THCICPedsPBIR %>% summarise(
  Name = "THCICPeds",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(TotalChildPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICBlackPedsPBIRSummary <- THCICBlackPedsPBIR %>% summarise(
  Name = "THCICBlackPeds",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(BlackChildPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICHispanicPedsPBIRSummary <- THCICHispanicPedsPBIR %>% summarise(
  Name = "THCICHispanicPeds",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(HispanicChildPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICWhitePedsPBIRSummary <- THCICWhitePedsPBIR %>% summarise(
  Name = "THCICWhitePeds",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(WhiteChildPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

# Adult

THCICAdultPBIRSummary <- THCICAdultPBIR %>% summarise(
  Name = "THCICAdult",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(TotalAdultPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICBlackAdultPBIRSummary <- THCICBlackAdultPBIR %>% summarise(
  Name = "THCICBlackAdult",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(BlackAdultPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICHispanicAdultPBIRSummary <- THCICHispanicAdultPBIR %>% summarise(
  Name = "THCICHispanicAdult",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(HispanicAdultPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

THCICWhiteAdultPBIRSummary <- THCICWhiteAdultPBIR %>% summarise(
  Name = "THCICWhiteAdult",
  TotalAREDV = sum(TotalEDCount),
  TotalPopAtRisk = sum(WhiteAdultPop),
  MeanAREDV = mean(TotalEDCount),
  SDAREDV = sd(PBIR),
  MedianAREDV = median(PBIR),
  IQRAREDV = IQR(PBIR),
  Min = min(PBIR),
  Max = max(PBIR)
)

## Bind Together
Summary <- rbind(ShootingsPBIRSummary, 
                 THCICPBIRSummary, 
                 THCICBlackPBIRSummary, 
                 THCICHispanicPBIRSummary,
                 THCICWhitePBIRSummary,
                 THCICPedsPBIRSummary,
                 THCICBlackPedsPBIRSummary,
                 THCICHispanicPedsPBIRSummary,
                 THCICWhitePedsPBIRSummary,
                 THCICAdultPBIRSummary,
                 THCICBlackAdultPBIRSummary,
                 THCICHispanicAdultPBIRSummary,
                 THCICWhiteAdultPBIRSummary)

write.csv(file = "Summary.csv", Summary)
```

# Poisson Total
```{r}
## Total Peds
PoissonTotal <- THCICEDCount %>% left_join(Covariates, by = "GEOID")

PoissonTotalModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(TotalPop + 1)),
  data = PoissonTotal,
  family = poisson(link = "log")
)

summary(PoissonTotalModel)

## Black Peds
PoissonBlackTotal <- THCICBlackEDCount %>% left_join(Covariates, by = "GEOID")

PoissonBlackTotalModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(BlackPop + 1)),
  data = PoissonBlackTotal,
  family = poisson(link = "log")
)

summary(PoissonBlackTotalModel)

## Hispanic Peds
PoissonHispanicTotal <- THCICHispanicEDCount %>% left_join(Covariates, by = "GEOID")

PoissonHispanicTotalModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(HispanicPop + 1)),
  data = PoissonHispanicTotal,
  family = poisson(link = "log")
)

summary(PoissonHispanicTotalModel)

## White Peds
PoissonWhiteTotal <- THCICWhiteEDCount %>% left_join(Covariates, by = "GEOID")

PoissonWhiteTotalModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(WhitePop + 1)),
  data = PoissonWhiteTotal,
  family = poisson(link = "log")
)

summary(PoissonWhiteTotalModel)

gc()
```

# Poisson Peds
```{r}
## Total Peds
PoissonPeds <- THCICPedsEDCount %>% left_join(Covariates, by = "GEOID")

PoissonPedsModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(TotalChildPop + 1)),
  data = PoissonPeds,
  family = poisson(link = "log")
)

summary(PoissonPedsModel)

## Black Peds
PoissonBlackPeds <- THCICBlackPedsEDCount %>% left_join(Covariates, by = "GEOID")

PoissonBlackPedsModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(BlackChildPop + 1)),
  data = PoissonBlackPeds,
  family = poisson(link = "log")
)

summary(PoissonBlackPedsModel)

## Hispanic Peds
PoissonHispanicPeds <- THCICHispanicPedsEDCount %>% left_join(Covariates, by = "GEOID")

PoissonHispanicPedsModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(HispanicChildPop + 1)),
  data = PoissonHispanicPeds,
  family = poisson(link = "log")
)

summary(PoissonHispanicPedsModel)

## White Peds
PoissonWhitePeds <- THCICWhitePedsEDCount %>% left_join(Covariates, by = "GEOID")

PoissonWhitePedsModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(WhiteChildPop + 1)),
  data = PoissonWhitePeds,
  family = poisson(link = "log")
)

summary(PoissonWhitePedsModel)

gc()
```

# Poisson Adult
```{r}
## Total Adult
PoissonAdult <- THCICAdultEDCount %>% left_join(Covariates, by = "GEOID")

PoissonAdultModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(TotalAdultPop + 1)),
  data = PoissonAdult,
  family = poisson(link = "log")
)

summary(PoissonAdultModel)

## Black Adult
PoissonBlackAdult <- THCICBlackAdultEDCount %>% left_join(Covariates, by = "GEOID")

PoissonBlackAdultModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(BlackAdultPop + 1)),
  data = PoissonBlackAdult,
  family = poisson(link = "log")
)

summary(PoissonBlackAdultModel)

## Hispanic Adult
PoissonHispanicAdult <- THCICHispanicAdultEDCount %>% left_join(Covariates, by = "GEOID")

PoissonHispanicAdultModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(HispanicAdultPop + 1)),
  data = PoissonHispanicAdult,
  family = poisson(link = "log")
)

summary(PoissonHispanicAdultModel)

## White Peds
PoissonWhiteAdult <- THCICWhiteAdultEDCount %>% left_join(Covariates, by = "GEOID")

PoissonWhiteAdultModel <- glm(
  TotalEDCount ~ log(ShootingsPBIR + 1) + o3 + no2 + pm10 + pm25 + so2 + poverty + no_vehicle + no_computer + no_insurance + less_than_hs_ed + natural_gas + resident_per_br + ten_units + two_br_or_less + unoccupied_housing + BlackPct + WhitePct + HispanicPct + offset(log(WhiteAdultPop + 1)),
  data = PoissonWhiteAdult,
  family = poisson(link = "log")
)

summary(PoissonWhiteAdultModel)

gc()
```
